### 2019-07-24 manuscript_clean.Rmd
VCV analysis methods section

In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset. This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].

>>>>

In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset. This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip]. In order to study correlations between the rates of evolution of each character, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv). When fitting all covariance terms simultaneously, we selected the largest set of characters that would allow the analysis to run without computational singularities. This excluded many of the morphometric characters which are linearly dependent on other characters. Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states. To test whether phenotypic integration changes across selective regimes determined by the reconstrcuted feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes. These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset. All the pairwise analyses were carried out transforming abstent states to zeroes. Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
